SoK: Web Application Attack Defenses (in Question)

### 2014-10-10 docs/questioning.tex
new category and entry
another entry

	\multirow{10}{*}{Policy Enforcement}

@@

	\multirow{10}{*}{Policy Enforcement}

>>>>

  \multirow{5}{*}{Securing Mashups}
  &   {\it {\sc om}ash}~\cite{CHC08} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} & {\sc csrf} \\
  &   {\it Mashup{\sc os}}~\cite{WFHJ07} & 149 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 1--59\% & {\sc xss} \\
	\multirow{7}{*}{Policy Enforcement}

@@

  \multirow{5}{*}{Securing Mashups}
  &   {\it {\sc om}ash}~\cite{CHC08} & {\sc na} & {\sc na} & {\sc na} \\
  &   {\it Mashup{\sc os}}~\cite{WFHJ07} & {\sc na} & {\sc na} & {\sc na} \\
	\multirow{7}{*}{Policy Enforcement}
